Proportional Occupancy

### 2021-07-06 R/PropOcDataThor.Rmd
this runs now on Thor

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)

```{r functions to get data}
#using the new 3D script with capped spheres.
source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') 
source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R')

GetPropOcData<-function(sampleName, xyDim,zDim){
  tic()
  #parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  sampleFolder<-paste0(parentFolder, sampleName)
  attrList<-str_split(sampleName,"_")[[1]]
  print(sampleName)
  fileList<-list.files(path = sampleFolder, full.names = TRUE)
  print(paste("# of files:", length(fileList)))
  if(length(fileList)<1){
    print("empty set")
    return(data.frame())
  }else{
  greenImg<-fileList[grep("G_",fileList)]
  redImg<-fileList[grep("R_",fileList)]
  propOcData<-AllDataPipeline(Slices2threeD(redImg),Slices2threeD(greenImg), 
                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
                                     sampleSize=10,xyRealDim=xyDim,
                                     zRealDim = zDim, pipeBinSize = 1)
  propOcData$Condition <- attrList[1]
  propOcData$TimePoint <- attrList[2]
  propOcData$Replicate <- attrList[3]
  toc()
  write.csv(propOcData, paste0("/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
  return(propOcData)}
  }

testGetPropOcData<-GetPropOcData("mono_d1_02", .415,.52)

testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)
testPmap<-pmap(list(metaData.df$SampleCode,metaData.df$xyDim, metaData.df$Zdim),
               GetPropOcData)
boundPmapTest<-bind_rows(testPmap)

@@

testGrep<-list.files(path = '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
testGrepG<-testGrep[grep("G_",testGrep)]

@@

testSlices2threeD<-Slices2threeD(testGrepG)
testGrepG[1]
testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))

>>>>

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library(EBImage)
library(tictoc)
library(stringr)
```

```{r functions to get data}
#using the new 3D script with capped spheres.
source('/home/jbarraza6/Documents/RScripts/PropOcFunctions2.0.R') #for Thor
source('/Users/jupabago/Documents/Whiteley/PROJECTS/Rpackage/PropOc Package/R/PropOcFunctions2.0.R') #for laptop

metaData.df <-read.csv('/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/images metadata.csv', header = TRUE)

GetPropOcData<-function(sampleName, xyDim,zDim){
  tic()
  parentFolder<- '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  #parentFolder<- '/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/'
  sampleFolder<-paste0(parentFolder, sampleName)
  attrList<-str_split(sampleName,"_")[[1]]
  print(sampleName)
  fileList<-list.files(path = sampleFolder, full.names = TRUE)
  print(paste("# of files:", length(fileList)))
  if(length(fileList)<1){
    print("empty set")
  }else{
  greenImg<-fileList[grep("G_",fileList)]
  redImg<-fileList[grep("R_",fileList)]
  propOcData<-AllDataPipeline(Slices2threeD(redImg),Slices2threeD(greenImg), 
                                     xydimSearch=round(30/xyDim),zdimSearch =round(30/zDim),
                                     sampleSize=10,xyRealDim=xyDim,
                                     zRealDim = zDim, pipeBinSize = 1)
  propOcData$Condition <- attrList[1]
  propOcData$TimePoint <- attrList[2]
  propOcData$Replicate <- attrList[3]
  write.csv(propOcData, paste0("/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/PropOc Data/",sampleName,".csv"))
  toc()}
  }

testGetPropOcData<-GetPropOcData("wt_d1_02", .415,.52)
testGetPropOcDataemptyFolder<-GetPropOcData("wt_d1_01", .415,.52)

blah<-pmap(list(metaData.df$SampleCode,metaData.df$xyDim, metaData.df$Zdim),
               GetPropOcData)
boundPmapTest<-bind_rows(testPmap)

@@

testGrep<-list.files(path = '/run/user/937561/gvfs/smb-share:server=130.207.66.142,share=raw_data/Confocal/Carolyn/2020/Chronic wounds/Binary Images/mono_d1_02', full.names = TRUE)
testGrepG<-testGrep[grep("G_",testGrep)]

@@

testSlices2threeD<-Slices2threeD(testGrepG)
testGrepG[1]
testImage1<-as.array(readImage(testGrepG[1], convert = TRUE))
install.packages("BiocManager")
BiocManager::install("EBImage")
```
